---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(MASS)
```

9. We will now consider the Boston housing data set, from the MASS library.

(a) Based on this data set, provide an estimate for the population mean of medv. Call this estimate μˆ.

```{r}
mean(Boston$medv)
```

(b) Provide an estimate of the standard error of μˆ. Interpret this result.
Hint: We can compute the standard error of the sample mean by dividing the sample standard deviation by the square root of the number of observations.

```{r}
sd(Boston$medv) /sqrt(length(Boston$medv))
```

(c) Now estimate the standard error of μˆ using the bootstrap. How does this compare to your answer from (b)?

```{r}
library(boot)
set.seed(1)
boot.fn <- function(data, index) {
    mu <- mean(data[index])
    return (mu)
}
boot(Boston$medv, boot.fn, 1000)
```

The bootstrap estimated standard error of u is very close to the estimate found in (b) of 0.4089.

(d) Based on your bootstrap estimate from (c), provide a 95 % con- fidence interval for the mean of medv. Compare it to the results obtained using t.test(Boston$medv).

```{r}
t.test(Boston$medv)
```

Okay, we have the confidence interval for the mean as 21.72953 and 23.33608.

```{r}
CI.mu.hat <- c(22.53 - 2 * 0.4119, 22.53 + 2 * 0.4119)
CI.mu.hat
```

Both the `t test` and the Bootstrap estimate are very close.

(e) Based on this dataset, provide an estimate of the median.

```{r}
median(Boston$medv)
```

(f) We would now like to estimate the standard error of u^med.Unfor- tunately, there is no simple formula for computing the standard error of the median. Instead, estimate the standard error of the median using the bootstrap. Comment on your findings.

```{r}
set.seed(1)
boot.fn <- function(data, index) {
  mu <- median(data[index])
  return(mu)
}
boot(Boston$medv, boot.fn, 1000)
```

We get an estimated median value of 21.2 which is equal to the value obtained in (e), with a standard error of 0.3874 which is relatively small compared to median value.

(g) Based on this data set, provide an estimate for the tenth per- centile of medv in Boston suburbs. Call this quantity μˆ0.1. (You can use the quantile() function.)

```{r}
quantile10 <- quantile(Boston$medv, 0.1)
quantile10
```

(h) Use the bootstrap to estimate the standard error of `quantile10`. Com- ment on your findings.

```{r}
boot.fn <- function(data, index) {
    mu <- quantile(data[index], c(0.1))
    return (mu)
}
boot(Boston$medv, boot.fn, 1000)
```

We get an estimated tenth percentile value of 12.75 which is again equal to the value obtained in (g), with a standard error of 0.5113 which is relatively small compared to percentile value.

