---
title: "Chapter5.2 Cross validation"
output: html_notebook
---

```{r}
library(tidyverse)
library(ISLR)
set.seed(1)
```

We continue to consider the use of a logistic regression model to
predict the probability of default using income and balance on the
Default data set. In particular, we will now compute estimates for
the standard errors of the income and balance logistic regression coefficients in two different ways: (1) using the bootstrap, and (2) using the standard formula for computing the standard errors in the glm()
function. Do not forget to set a random seed before beginning your
analysis.

(a) Using the summary() and glm() functions, determine the estimated
standard errors for the coefficients associated with income
and balance in a multiple logistic regression model that uses
both predictors.

```{r}
set.seed(1)
model <- glm(default ~ income + balance, data = Default, family = "binomial")
summary(model)
coeff <- coef(summary(model))
```

The standard errors for the model are respectively `r coeff[1,2]`, `r coeff[2,2]` and `r coeff[3,2]` for the intercept, `income` and `balance` variables.

(b) Write a function, boot.fn(), that takes as input the Default data
set as well as an index of the observations, and that outputs the coefficient estimates for income and balance in the multiple logistic regression model.

```{r}
boot.fn <- function(data, index) {
    fit <- glm(default ~ income + balance, data = data, family = "binomial", subset = index)
    return (coef(fit))
}
```

(c) Use the boot() function together with your boot.fn() function to
estimate the standard errors of the logistic regression coefficients
for income and balance.

```{r}
library(boot)
boot(Default, boot.fn, 1000)
```

(d) Comment on the estimated standard errors obtained using the
glm() function and using your bootstrap function

The estimated standard errors obtained by the two methods are pretty close. 
